DRAM and ES

### 2021-01-19 02-supply-chain.Rmd
adding link to the lucidchart

---
title: "Supply chain Axis"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: 02-supply-chain.bib
bibliography: library.bib
#nocite: '@*'

@@

>>>>

---
title: "DRAM and ES"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: 02-supply-chain.bib
bibliography: library.bib
#nocite: '@*'

@@

[**Link to modify the Graph**](https://lucid.app/lucidchart/invitations/accept/f6847ab0-3fd4-4749-a581-669058760d2d)
